Time delay estimation in unresolved lensed quasars

### 2020-12-29 paper/aa-package/paper.tex
update

	\caption[cm]{Top-left: distribution of known GLQs as a function of the number of multiple images. Top-right: distribution of known GLQs as a function of the maximum angular separation. Bottom (left and right): Magnitude of the multiple images versus the maximum image separation. The grey region contains 70$\%$ of the total GLQ sample.}

@@

The paper is structured as follows: Sec. \ref{sec:MC} describes the Monte Carlo (MC) simulations we performed.... Sec 3...

@@

%-------------------------------------- Two column figure (place early!)
   \begin{figure*}
   \centering
   %%%\includegraphics{empty.eps}
   %%%\includegraphics{empty.eps}
   %%%\includegraphics{empty.eps}
   \caption{Adiabatic exponent $\Gamma_1$.
               $\Gamma_1$ is plotted as a function of
               $\lg$ internal energy $\mathrm{[erg\,g^{-1}]}$ and $\lg$
               density $\mathrm{[g\,cm^{-3}]}$.}
              \label{FigGam}%
    \end{figure*}
%
   In this section the one-zone model of \citet{baker},
   originally used to study the Cephe{\"{\i}}d pulsation mechanism, will
   be briefly reviewed. The resulting stability criteria will be
   rewritten in terms of local state variables, local timescales and
   constitutive relations.

   \citet{baker} investigates the stability of thin layers in
   self-gravitating,
   spherical gas clouds with the following properties:
   \begin{itemize}
      \item hydrostatic equilibrium,
      \item thermal equilibrium,
      \item energy transport by grey radiation diffusion.
   \end{itemize}
   For the one-zone-model Baker obtains necessary conditions
   for dynamical, secular and vibrational (or pulsational)
   stability (Eqs.\ (34a,\,b,\,c) in Baker \citeyear{baker}). Using Baker's
   notation:

>>>>

	\caption[cm]{Top-left: distribution of known GLQs as a function of the number of multiple images. Top-right: distribution of known GLQs as a function of the maximum image separation. Bottom (left and right): Magnitude of the multiple images versus the maximum image separation. The grey region contains 70$\%$ of the total GLQ sample.}

@@

The paper is structured as follows: Sec. \ref{sec:idea_and_method description} describes the ML-based method we use for evaluating the time delay between multiple images. Sec. \ref{sec:MC} describes the Monte Carlo (MC) simulations needed to train our ML algorithm. Sec. \ref{sec:test_approach} shows the results of our method in a test dataset obtained by simulating the real systems RXJ1131. Finally, Sec. \ref{sec:real_data} shows our evaluated time delays for real systems and compare it with other estimations.

\section{Time delay estimation with ML technique} \label{sec:idea_and_method description}

@@

\section{Test approach on fake dataset} \label{sec:test_approach}

\section{Results on real data} \label{sec:real_data}

%-------------------------------------- Two column figure (place early!)
   \begin{figure*}
   \centering
   %%%\includegraphics{empty.eps}
   %%%\includegraphics{empty.eps}
   %%%\includegraphics{empty.eps}
   \caption{Adiabatic exponent $\Gamma_1$.
               $\Gamma_1$ is plotted as a function of
               $\lg$ internal energy $\mathrm{[erg\,g^{-1}]}$ and $\lg$
               density $\mathrm{[g\,cm^{-3}]}$.}
              \label{FigGam}%
    \end{figure*}
%

   params
